Temporal and Spatial Analysis of Hate Crimes in Toronto

### 2024-09-25 paper/paper.qmd
editted the observation section

The data section will introduced the detail of the data set used in this research in @sec-data -- Data. The variables as well as the cleaning process will be discussed in this section. The result section @sec-results will focus on the findings and the visualization of the analysis. The discussion session @sec-discussion talks about the limitation of this research and potential error caused by research design or the natural form of data. lastly, the conclusion part raps up the discovers and summarizes all the findings into a short paragraph.

@@

## Measurement and packages {#sec-measurement and packages}
The Data set used in the analysis is gathered from Open Data Toronto through the Open Data Toronto [@opendatatoronto] and used the statistical software R [@citeR] for importing data, data cleaning and testing data. The data source "Crime Data" is used from [@open-data-set] collected from Toronto Police starting from 2018 to the end of 2023. It includes both temporal and spatial attributes. Other packages were used for analyzing the data such as ggplot [@ggplot2], tidyverse [@tidyverse], lubridate [@lubridate], dplyr [@dplyr],tinytex [@tinytex].

@@

## Data cleaning {#sec-data cleaning}

@@

```

>>>>

The data section will introduced the detail of the data set used in this research in @sec-data -- Data. The variables as well as the cleaning process will be discussed in this section. @sec-results will focus on the findings and the visualization of the analysis. @sec-discussion talks about the limitation of this research and potential error caused by research design or the natural form of data. lastly, the conclusion part raps up the discovers and summarizes all the findings into a short paragraph.

@@

## Measurement and packages 
The Data set used in the analysis is gathered from Open Data Toronto through the Open Data Toronto [@opendatatoronto] and used the statistical software R [@citeR] for importing data, data cleaning and testing data. The data source "Crime Data" is collected from Toronto Police starting from 2018 to the end of 2023. It includes both temporal and spatial attributes. Other packages were used for analyzing the data such as ggplot [@ggplot2], knitr[@knitr], tidyverse [@tidyverse], lubridate [@lubridate], tinytex[@tinytex], dplyr [@dplyr].

@@

## Data cleaning

@@

# Group by NEIGHBOURHOOD_158 and count the number of hate crimes for each neighborhood
neighborhood_crime_count <- analysis_data %>%
  group_by(NEIGHBOURHOOD_158) %>%
  summarise(Crime_Count = n()) %>%
  arrange(desc(Crime_Count))

# Display the resulting table
print(neighborhood_crime_count)
```
